---
title: "Assignment 3"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r}
library(ggplot2)
```


```{r}
# Run the following code in R-studio to create two variables X and Y. 

set.seed(2017) 
X=runif(100)*10 
Y=X*4+3.45 
Y=rnorm(100)*0.29*Y+Y 
```
# a)Plot Y against X.Based on the plot do you think we can fit a linear model to explain Y based on X?
```{r}
# Plot Y against X.

plot(X,Y, main = "Plotting Y aginst X", xlab = "X axis", ylab = "Y axis",frame = FALSE)
# Add regression line
abline(lm(Y~X), col = "red")
```

# Interpretation:

We can see there exists correlation between the variables "x" and "y" from the plot. Hence linear model would be a good fit.

# b)Construct a simple linear model of Y based on X. Write the equation that explains Y based on X. What is the accuracy of this model?
```{r}
# Y=4.4655+3.6108*X
# Accuracy is 0.6517 or 65%
linear_mod <- lm(Y~X)
summary(linear_mod)

# Regression visualization
plot(X, Y, xlab = "X axis", 
     ylab = "Y axis",
     main = "Regression Visualization")
abline(4.4655, 3.6108, col = "red")
```

# c)How  the  Coefficient  of  Determination,  R2,  of  the  model  above  is  related  to  the  correlation coefficient of X and Y? 
```{r}
cor(X,Y)^2

```

# Interpretation:

The coefficient of determination, $R^2$, of the above model is similar to the coefficient of X and Y, which is around 65%

# Question 2:
# a)James wants to buy a car. He and his friend, Chris, have different opinions about the Horse Power (hp) of cars. James think the weight of a car (wt) can be used to estimate the Horse Power of the car while Chris thinks the fuel consumption expressed in Mile Per Gallon (mpg), is a better estimator of the (hp). Who do you think is right? Construct simple linear models using mtcars data to answer the question. 
```{r}
head(mtcars)
```

Simple Linear model according to James
```{r}
plot(mtcars$wt, mtcars$hp, main = "J_model",
     xlab = "wt", ylab = "hp",frame = FALSE)
# Add regression line
abline(lm(mtcars$hp ~ mtcars$wt), col = "blue")
J_model <- lm(formula = hp~wt, data = mtcars)
summary(J_model)
# Accuracy of J_model is 0.4339
```

Simple Linear model according to Chris
```{r}
plot(mtcars$mpg, mtcars$hp, main = "C_model",
     xlab = "mpg", ylab = "hp",frame = FALSE)
# Add regression line
abline(lm(mtcars$hp ~ mtcars$mpg), col = "blue")
C_model <- lm(formula = hp~mpg, data = mtcars)
summary(C_model)
# Accuracy of C_model is 0.6024
```

# Interpretation:

We can see the value of C_model is fairly accurate. so,Chris' opinion is right (i.e)the fuel consumption expressed in Mile Per Gallon (mpg), is a better estimator of the (hp).

# b)Build a model that uses the number of cylinders (cyl) and the mile per gallon (mpg) values of a car to predict the car Horse Power (hp). Using this model, what is the estimated Horse Power of a car with 4 calendar and mpg of 22? 
```{r}
H_model <- lm(formula = hp~cyl+mpg, data = mtcars)
summary(H_model)
Esti_hp <- predict(H_model,data.frame(cyl=4,mpg=22))
Esti_hp
```

# Interpretation:

The estimated Horse Power of a car with cyl = 4 and mpg = 22 is 88.93

# Question 3
```{r}
library(mlbench)
data("BostonHousing")
View(BostonHousing)

# Plotting all the variable using box plot to observe how the values of the various variables in the dataset have changed over time. 
boxplot(BostonHousing[,c(1,2,4,11,14)])
```

# a) Build a model to estimate the median value of owner-occupied homes(medv) based on the following variables:crime crate (crim),proportion of residential land zoned for lots over 25,000 sq.ft(zn), the local  pupil-teacher ratio(ptratio) and weather the whether  the tract bounds Chas River(chas). Is this an accurate model?(Hint check R2 ) 
```{r}
set.seed(125)
owner_model <- lm(formula = medv~crim+zn+ptratio+chas,data = BostonHousing)
summary(owner_model)
owner_model
```

# Interpretation:

The accuracy of owner_model is 0.3599, which means the model is not accurate enough.

# b) Use the estimated coefficient to answer these questions?  

# I. Imagine two houses that are identical in all aspects but one bounds the Chas River and the other does not. Which one is more expensive and by how much? 

Answer:

 The estimated coefficient of chas1 is 4.58393. chas is the factor of two variable 0 and 1, one bound Chas River is 1 and if it doesn't it is 0. It is given that the median value of owner-occupied homes is 1000 dollars. when multiplied with coefficient(4.58393*1000), the result is 4583.93$ which is expensive.

# II. Imagine two houses that are identical in all aspects but in the neighborhood of one of them the pupil-teacher ratio is 15 and in the other one is 18. Which one is more expensive and by how much? (Golden Question) 

Answer:

 It is clear that for every single unit increase in ptratio, price of houses is decreased by 1.49367 (i.e) 1493.67 (in thousands).If ptratio is 15, then it will be decrease of 15 * 1493.67= 22405.05. Likely, if ptratio is 18 then it will be a decrease of18*1493.67 = 26886.06. Finally, if ptratio of 15 expensive by $4481.01 when comapred to ptratio of 18. 

# c) Which of the variables are statistically important (i.e. related to the house price)? Hint: use the p-values of the coefficients to answer. 

Answer:

 The P-values are not equal to 0. so, we can reject the null hypothesis and conclude that there is no relationship between house price and other factors in the model. Hence, each variable has statistical significance.
 
# d) Use the anova analysis and determine the order of importance of these four variables. 
```{r}
anova(owner_model)
```
# Interpretation:

 As we can see, the crim variable explains substantially more variability(sum squared) than the other variables. This could be explained by the model being greatly enhanced by the addition of the crim. However, residuals demonstrate that a significant fraction of the variability is unaccounted for.

 The order of importance is crim,ptratio,zn,chas



 